Phenotype and risk assesment of insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-09-09 analysis/paper/paper.Rmd
V2.2 - figure height fix

```{r rfplot, fig.cap="Therapy of anaphylaxis. A: Adrenaline use considering if patients had previous anaphylaxis. B: Variable impo"}
ggarrange(
  adren_prev+
    geom_segment(aes(x = 0.5,
                     xend = 2.5,
                     y = 0.33,
                     yend = 0.33),
                 color="white",
                 linetype =2),
  rf_ggplot_treatment,
  nrow = 1,
  ncol = 2,
  labels=c("A","B")
)
```

>>>>

```{r rfplot, fig.cap="Therapy of anaphylaxis. A: Adrenaline use considering if patients had previous anaphylaxis. B: Variable impo", fig.height=3.5, fig.width=7.1}
ggarrange(
  adren_prev+
    geom_segment(aes(x = 0.5,
                     xend = 2.5,
                     y = 0.33,
                     yend = 0.33),
                 color="white",
                 linetype =2),
  rf_ggplot_treatment,
  nrow = 1,
  ncol = 2,
  labels=c("A","B"),
  widths = c(1,1.3)
)
```
